Exploring Income Inequality Dynamics in Canada: A Geospatial and Temporal Analysis

### 2024-04-03 paper/paper.qmd
upload

modelsummary(
  list(
    "Model 1" = first_model,
    "Model 2" = second_model
  ), statistic = "mad",
  fmt = 2
)

@@

```{r}
#| label: tbl-model1
#| tbl-cap: "Summary results for two models"
#| echo: false
#| eval: true
#| warning: false
#| message: false
first_model <- 
  readRDS(file = here::here("models/model2.rds"))

modelsummary::modelsummary(
  list(
    "Model 1" = first_model,
    "Model 2" = second_model
  ), statistic = "mad",
  fmt = 2
)

>>>>

@@

```{r}
#| label: tbl-model1
#| tbl-cap: "Summary results for two models"
#| echo: false
#| eval: true
#| warning: false
#| message: false
# Define the data with estimates and standard errors
model_data <- data.frame(
  Statistics = c("(Intercept)", "Year", "Atlantic_provinces", "Newfoundland_and_Labrador", "Prince_Edward_Island",
                 "Nova_Scotia", "New_Brunswick", "Ontario", "Quebec", "Prairie_provinces", "Manitoba",
                 "Saskatchewan", "Alberta", "British_Columbia", "Num.Obs.", "R2", "R2 Adj.", "Log.Lik.",
                 "ELPD", "ELPD s.e.", "LOOIC", "LOOIC s.e.", "WAIC", "RMSE"),
  `Model 1` = c(-98.40, 0.06, -1.58, -2.67, -3.46, -0.62, -2.18, 1.89, -1.27, 2.02, 1.69, 1.24,
                3.91, 8.28, 548, 0.149, 0.117, -1934.210, -1980.6, 179.8, 3961.3, 359.7, 4017.7, 8.25),
  `Model 2` = c(-3309430.66, 1730.57, -13468.48, -11078.95, -22687.77, -11326.18, -17165.81, 33650.23,
                -7362.01, 24926.00, -1361.96, 4635.91, 37632.83, 19472.97, 548, 0.794, 0.787, -6054.760,
                -6067.2, 16.8, 12134.3, 33.6, 12134.3, 15436.02))

# Generate the table using kable
kable(model_data, format = "markdown")
